Geometric Signs on Paleolithic Mobile Objects as Cultural Group Markers

### 2025-02-04 endofquarterpaper.qmd

```{r}
## clean the data
library(tidyverse)
library(magrittr)
library(rcarbon)
signbase_full <- read_csv("data/signBase_Version1.0.csv")
nsites <- signbase_full %>% 
  pull(site_name ) %>% 
  unique() %>% 
  length()
nartifacts <- nrow(signbase_full)
ncountries <- signbase_full %>% 
  pull(country) %>% 
  unique() %>% 
  length()
nsigntypes <- ncol(signbase_full)
signbase_full_clean <- signbase_full %>% 
  filter(site_name != "Willendorf",
         site_name != "Riparo di Fontana Nuova",
         site_name != "Muralovka",
         site_name != "Shanidar Cave",
         site_name != "Hayonim Cave",
         site_name != "El Salitre",
         site_name != "Grotte De La Princesse Pauline",
         site_name != "Šandalja II") %>% 
  dplyr::select(-other, -rectangle)
nsites_clean <- signbase_full_clean%>% 
  pull(site_name ) %>% 
  unique() %>% 
  length()
nartifacts_clean <- nrow(signbase_full_clean)
ncountries_clean <- signbase_full_clean %>% 
  pull(country) %>% 
  unique() %>% 
  length()
nsigntypes_clean <- nsigntypes - 1
signbase_years <- signbase_full_clean %>% 
  drop_na(date_bp_max_min) %>% 
  mutate(date_bp_max_min = str_replace_all(date_bp_max_min, "\\+\\/\\-", "±")) %>% 
  mutate(date_bp_max_min = str_replace_all(date_bp_max_min, "\\+", "±")) %>% 
  separate(date_bp_max_min,
           sep = " - ",
           c("date_bp_max", "date_bp_min"),
           remove = FALSE) %>% 
  mutate(date_bp_max = ifelse(str_detect(date_bp_max, "\\/"),
                              str_extract(date_bp_max, ".*?(?=\\/)"),
                              date_bp_max)) %>% 
  mutate(date_bp_min = ifelse(str_detect(date_bp_min, "\\/"),
                              str_extract(date_bp_min, ".*?(?=\\/)"),
                              date_bp_min)) %>% 
  separate(date_bp_max,
           sep = "±",
           c("date_bp_max_age",
             "date_bp_max_error")) %>% 
  separate(date_bp_min,
           sep = "±",
           c("date_bp_min_age",
             "date_bp_min_error")) %>% 
  drop_na(date_bp_max_age,
          date_bp_max_error) %>% 
  mutate(date_bp_max_age = parse_number(date_bp_max_age),
         date_bp_max_error = parse_number(date_bp_max_error))
signbase_years_cal <- 
  rcarbon::calibrate(signbase_years$date_bp_max_age,
            signbase_years$date_bp_max_error,
            verbose = FALSE) %>% 
  summary() %>% 
  data_frame()
pretty_print_dates <- 
  function(x) formatC(x, 
                      decimal.mark=".", 
                      big.mark=",", 
                      digits = 0, 
                      format = "f")
date_min <- signbase_years_cal %>% 
  pull(MedianBP) %>% 
  min()
date_max <- signbase_years_cal %>% 
  pull(MedianBP) %>% 
  max()
date_range <- date_max - date_min
date_min_pretty <- pretty_print_dates(date_min)
date_max_pretty <- pretty_print_dates(date_max)
date_range_pretty <- pretty_print_dates(date_range)
```

>>>>

```{r}
## clean the data
library(tidyverse)
library(magrittr)
library(rcarbon)
library(readxl)
signbase_full <- read_csv("data/signBase_Version1.0.csv")
nsites <- signbase_full %>% 
  pull(site_name ) %>% 
  unique() %>% 
  length()
nartifacts <- nrow(signbase_full)
ncountries <- signbase_full %>% 
  pull(country) %>% 
  unique() %>% 
  length()
nsigntypes <- ncol(signbase_full)
signbase_full_clean <- signbase_full %>% 
  filter(site_name != "Willendorf",
         site_name != "Riparo di Fontana Nuova",
         site_name != "Muralovka",
         site_name != "Shanidar Cave",
         site_name != "Hayonim Cave",
         site_name != "El Salitre",
         site_name != "Grotte De La Princesse Pauline",
         site_name != "Šandalja II") %>% 
  dplyr::select(-other, -rectangle)
nsites_clean <- signbase_full_clean%>% 
  pull(site_name ) %>% 
  unique() %>% 
  length()
nartifacts_clean <- nrow(signbase_full_clean)
ncountries_clean <- signbase_full_clean %>% 
  pull(country) %>% 
  unique() %>% 
  length()
nsigntypes_clean <- nsigntypes - 1
signbase_years <- signbase_full_clean %>% 
  drop_na(date_bp_max_min) %>% 
  mutate(date_bp_max_min = str_replace_all(date_bp_max_min, "\\+\\/\\-", "±")) %>% 
  mutate(date_bp_max_min = str_replace_all(date_bp_max_min, "\\+", "±")) %>% 
  separate(date_bp_max_min,
           sep = " - ",
           c("date_bp_max", "date_bp_min"),
           remove = FALSE) %>% 
  mutate(date_bp_max = ifelse(str_detect(date_bp_max, "\\/"),
                              str_extract(date_bp_max, ".*?(?=\\/)"),
                              date_bp_max)) %>% 
  mutate(date_bp_min = ifelse(str_detect(date_bp_min, "\\/"),
                              str_extract(date_bp_min, ".*?(?=\\/)"),
                              date_bp_min)) %>% 
  separate(date_bp_max,
           sep = "±",
           c("date_bp_max_age",
             "date_bp_max_error")) %>% 
  separate(date_bp_min,
           sep = "±",
           c("date_bp_min_age",
             "date_bp_min_error")) %>% 
  drop_na(date_bp_max_age,
          date_bp_max_error) %>% 
  mutate(date_bp_max_age = parse_number(date_bp_max_age),
         date_bp_max_error = parse_number(date_bp_max_error))
signbase_years_cal <- 
  rcarbon::calibrate(signbase_years$date_bp_max_age,
            signbase_years$date_bp_max_error,
            verbose = FALSE) %>% 
  summary() %>% 
  data_frame()
pretty_print_dates <- 
  function(x) formatC(x, 
                      decimal.mark=".", 
                      big.mark=",", 
                      digits = 0, 
                      format = "f")
date_min <- signbase_years_cal %>% 
  pull(MedianBP) %>% 
  min()
date_max <- signbase_years_cal %>% 
  pull(MedianBP) %>% 
  max()
date_range <- date_max - date_min
date_min_pretty <- pretty_print_dates(date_min)
date_max_pretty <- pretty_print_dates(date_max)
date_range_pretty <- pretty_print_dates(date_range)
```
